Notes on the low density parameters in {\tt MAESTRO}

### 2012-05-18 docs/lo_density/lo_density.tex
fix notes to talk about when we don't hit cutoff density

\subsection{Multilevel Planar}
In this case, the base state exists as several one-dimensional arrays, each with
different grid spacing.  Refer to Figure \ref{Fig:Cutoff_Multi} in the following examples.
The guiding principle is to check whether $\rho_0$ falls below $\rho_{\rm cutoff}$ on the finest
grid first.  If not, check the next coarser level.  Continue until you reach the base grid,
in which case $\rho_0$ must fall below $\rho_{\rm cutoff}$ somewhere.  Some examples are in order:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=2.0in]{\lodensfigpath/cutoff_multi}\hspace{0.2in}
\caption{Multilevel cutoff density example.}
\label{Fig:Cutoff_Multi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\item In {\tt init\_base\_state}, we give a warning if {\tt anelastic\_cutoff}
  is smaller than the minimum model density.  Then, if ${\tt anelastic\_cutoff} 
  < {\tt base\_cutoff\_density}$, we abort the program.

@@

\item In {\tt init\_base\_state}, we give a warning of {\tt base\_cutoff\_density}
  is smaller than the minimum model density.  Then, if ${\tt anelastic\_cutoff} 
  < {\tt base\_cutoff\_density}$ we abort the program.

>>>>

\subsection{Multilevel Planar}
In this case, the base state exists as several one-dimensional arrays, each with
different grid spacing.  Refer to Figure \ref{Fig:Cutoff_Multi} in the following examples.
The guiding principle is to check whether $\rho_0$ falls below $\rho_{\rm cutoff}$ on the finest
grid first.  If not, check the next coarser level.  Continue until you reach the base grid.
Some examples are in order:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=2.0in]{\lodensfigpath/cutoff_multi}\hspace{0.2in}
\caption{Multilevel cutoff density example.}
\label{Fig:Cutoff_Multi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Note: if $\rho_0$ does not fall below $\rho_{\rm cutoff}$ at any level, we set the cutoff 
coordinate at the fine level to be first first cell above the domain and propagate the 
coordinate to the coarser levels.

@@

@@
